Open Policing Project: Prima Facie Stats

### 2018-12-15 lib/bunching_report.Rmd
Add FL

@@

\>20 MPH over: \$304

>>>>

# Original FL data

Bunching point at 9MPH

```{r ok, fig.height=3.75, fig.width=7}
tbl <- haven::read_dta(here::here("data", "bunching", "Cite_05_15_Use.dta")) %>% 
  rename(
      subject_race = Race,
      subject_age = Age,
      officer_id = OfficerId, 
      speed = ActualSpeed, 
      posted_speed = PostedSpeed,
      vehicle_make = VehicleMake
    ) %>% 
  mutate(subject_race = plyr::mapvalues(
    subject_race, 
    from = c("B", "H", "W"), 
    to = c("black", "hispanic", "white")
  ))
tbl <-
  tbl %>%
  mutate(
    age_group = as.integer(subject_age / 10),
    hour_of_day = if_else(Hour == 99, NA_real_, Hour)
  )
bt <- bunching_test(
  tbl,
  CountyNum,
  hour_of_day,
  age_group,
  vehicle_make,
  over_limit = over_limit,
  bunching_points = c(9)
)
display(bt)
kable(bt$results$difference_in_difference)
```

@@

20 MPH over: \$304
